An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-04-24 Article/EconGrowth2.Rnw
Now correctly setting levels (with relevel) for the Country column of historical data. Fixes Issue #101.

# Pull in some constants and other important functions
source("Scripts/files.R")

# ********************************************************
# We need to define a directory path to the resample data results from "Article"
archive <- file.path("..", "data_resample_2014-04-24_Refactored-Code_n=1000.zip")
baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# ********************************************************
# Load the fits to the original historical data out of the archive we're using.
# This object should be passed in to functions that need specific fits.
f <- gzcon(unz(archive, file.path(baseResample, "oModels.Rdata")))
oModels <- readRDS(f)
close(f)
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")

@@

<<constants, include=FALSE>>=
source(file.path("..", "Scripts", "Constants.R"))

# Graph Heights
maxHeight <- 8.5 # Inches
ninePanelScatterGraphHeight <- maxHeight # Inches
# ninePanelTernaryGraphHeight <- 7 # Inches
# ninePanelSpaghettiGraphHeight <- 7 # Inches

@@

\twocolumn{}
<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
historicalData <- read.table(file=file.path(baseHistorical, "AllData.txt"), header=TRUE)
levels(historicalData$Country) <- countryAbbrevs
historicalPlot(historicalData)
@

>>>>

# Pull in some constants and other important functions
source("Scripts/files.R")
source(file.path("..", "Scripts", "Constants.R"))

# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
baseHistorical <- file.path("..", "data")
historicalData <- read.table(file=file.path(baseHistorical, "AllData.txt"), header=TRUE)
# Adjust the levels of historicalData so that the levels are in the same order as countryAbbrevs.
for (lev in rev(countryAbbrevs)){
  historicalData$Country <- relevel(historicalData$Country, ref=lev)
}

# Set up for loading resample results
# We need to define a directory path from "Article" to the resample data results
archive <- file.path("..", "data_resample_2014-04-24_Refactored-Code_n=1000.zip")
baseResample <- "data_resample" # Define the directory within the archive wherein we can find the data.
# Load the fits to the original historical data out of the archive we're using.
# This object (oModels) should be passed in to functions that need information from orig fits.
f <- gzcon(unz(archive, file.path(baseResample, "oModels.Rdata")))
oModels <- readRDS(f)
close(f)

@@

<<constants, include=FALSE>>=
# Graph Heights
maxHeight <- 8.5 # Inches
ninePanelScatterGraphHeight <- maxHeight # Inches
# ninePanelTernaryGraphHeight <- 7 # Inches
# ninePanelSpaghettiGraphHeight <- 7 # Inches

@@

\twocolumn{}
<<Historical_Graph, fig.pos="H", fig.align='center', fig.width=3, fig.height=7.5, fig.cap="Historical data: indexed GDP ($y$), capital stock ($k$), labor ($l$), and thermal energy ($q$).">>=
historicalPlot(historicalData)
@
